NPH-MS-2020-34477 - Response to reviewers

### 2020-11-02 README.Rmd
readme pic 🌼🏔️
1st major revision 🍃

![Picos de Europa National Park, Cantabrian Mountains, Spain](data/fernandezpascual/Picos de Europa.JPG)

@@

This repository stores all the information related to the publication *The seed germination spectrum of alpine plants: a global meta-analysis*, including the raw datasets, the scripts to perform data cleaning and analysis, and the `Rmarkdown` files to create the manuscript.

@@

* `data` Original raw files including primary germination data and species traits.
* `doc` Files to create the manuscript using `Rmarkdown`.
* `results` Output of the `R` scripts, including clean data and MCMCglmm analysis outputs.
* `src` Scripts in `R` language used to clean the raw data and perform the analyses of the manuscript.

@@

Please cite the dataset as `CITATION`

>>>>

![Picos de Europa National Park, Cantabrian Mountains, Spain](Picos de Europa.jpg)

@@

This repository stores all information related to the manuscript *The seed germination spectrum of alpine plants: a global meta-analysis*, including raw data, `R` scripts to process and analyse data, and `Rmarkdown` files to create the manuscript.

@@

* `data` Primary germination data and species traits.
* `doc` Files to create the manuscript using `Rmarkdown`.
* `results` Output of the `R` scripts, including MCMCglmm analysis outputs.
* `src` Scripts in `R` language used to process data and perform the analyses of the manuscript.

@@

Please cite this repository as `The seed germination spectrum of alpine plants: a global meta-analysis. Manuscript in preparation.`

### 2020-11-02 doc/cover-letter.Rmd
1st major revision 🍃

---
title: "NPH-MS-2020-34477 - Response to reviewers"
date: "`r format(Sys.time(), '%d/%m/%Y')`"
output: word_document
bibliography: refs.bib
csl: new-phytologist.csl
link-citations: yes
always_allow_html: true
---

@@

We respond below to each of the issues pointed out by the referees. We have adopted most of the proposed changes. Regarding light, we explain that this is an intrinsic limitation of the meta-analysis approach, and discuss the implications. As for the phylogenetic signal, we explain that this is explicitly taken into account by adopting a phylogenetic comparative statistical method such as the MCMCglmm, which considers phylogeny and phylogenetic signal within the analysis.

@@

We have changed the introductory point to *Given the micro-climatic heterogeneity of alpine landscapes, and the wealth of local studies on alpine seed ecology, a current challenge is to synthesize, at the global level, the seed ecological spectrum of alpine plants.*.

@@

The effects that are missing are those that overlap with zero (i.e. no effect) and also have very wide credible intervals (much wider than the other cues). They hamper the figure's visibility (i.e. they make all other effects appear too compressed), so we removed them from the plots. We have included this clarification in the figure's caption.

@@

We have moved the call to the section's beginning and labelled the axes. Indicating to which panel we are referring to in the text is not easy, because the different panels/traits are intertwined in the descriptions, therefore it would require to make many recurrent calls (and, in our opinion, that would burden the text too much.)

@@

Yes, there is a knowledge gap for tropical mountains. We were unable to find any significant amount of data from the tropics (excluding single species studies). We have qualified *global* as excluding the tropics throughout the manuscript, and commented on the knowledge gap in the conclusions.

@@

The referee is right that light is a more complex cue than the binary variable we considered. The same can be said about other cues, like alternating temperature (amplitude of the alternation, duration of the cycles...) or cold stratification (actual temperature, length...). However, to conduct a meta-analysis, we need to find a compromise between data quality and quantity. Detailed descriptions of light spectral composition and photoperiod are only available for a small fraction of the whole dataset. Therefore, we must summarise cues into some variables (like light absence/presence) that are routinely recorded in the majority of trials. We have added these considerations to the conclusions.

@@

We considered storage type as a continuum (i.e. embryo:seed ratio), ranging from species with small embryos with copious endosperm (often referred to as endospermic) to species with no endosperm at all and all nutrient reserves stored in the embryo (often referred to as non-endospermic seeds). To improve understanding, we have included a definition of non-endospermic seeds as *non-endospermic seeds that store nutrients in the cotyledons*. In any comparative biology analysis, all traits are always phylogenetically confounded. This is why we used a phylogenetic comparative analysis such as the MCMCglmm. The analysis includes, as a random factor, a matrix of phylogenetic distances among species. In this way, traits are analysed in relation to the underlying phylogenetic structure of the dataset. In our models, both the trait (seed:endosperm ratio) and phylogeny had significant effects. The use of phylogenetic comparative analysis is covered in the analysis section of the methods section.

@@

In our manuscript we use the definition and classification of dormancy that is currently dominant in seed ecology and physiology. This framework is based on two main references: (i) the concept by Vleeshouwers et al. [-@RN3254] that dormancy is an inner seed property ("endodormancy"), which should be separated from the absence of appropriate germination cues in the environment ("ecodormancy"); and the classification system proposed by Baskin & Baskin [-@RN3261] based on previous work by Nikolaeva et al. [-@RN2877] and which considers morphological and physical dormancy separated from physiological. There are two practical reasons to use this framework: first, it will be readily understandable to the widest scope of readers; and second, it provides the largest amount of species trait data available [@RN3214; @RN4743]. We have retained the definition and classification of dormancy originally used in our paper, however, we have also included explanation in the text of how this classification corresponds to the terminology preferred by the reviewer.

@@

We have revised the entire conclusions paragraph to address these concerns, being more specific about both the conclusions and about the limitations of the data.

@@

The referee is right and we have screened the text for this class of words. *Change* is used to refer to a concept like climate change, or to encompass and summarise changes that can go in different directions (environmental changes, snow cover changes). *Interplay* and *intertwined* are used in places like the summary and conclusions, where we must summarise concepts that are detailed elsewhere. *Interaction* is used in its statistical meaning, and qualified as *no interaction*, *negative interaction*, etc. We could not find *vary*. Regarding the specific point at L523, this is not a neutral statement: the direction of *interplay* is explained in the same sentence, after the *;*. To make this point clear, we have substituted the *;* with a *:*.

@@

We have removed wind.

@@

We have removed the *soap*, and now the two introductory sentences link directly to former L73.

@@

To the latter. To be more concrete, we have changed the sentence to *Given the high micro-climatic heterogeneity of alpine landscapes, and the wealth of local studies on alpine seed ecology (reviewed in the following paragraphs), a current challenge is to synthesize, at the global level, the seed ecological spectrum of alpine plants*.

@@

We have removed the reference to a hard set depth boundary. The depth profile of temperature fluctuations will depend on soil type, vegetation cover, snow cover. Specifically, the insulating effect of snow cover means that fluctuation of T is not necessarily the norm. We have changed the sentence to *Fluctuations of diurnal temperature decrease with increasing burial depths and the depth profile of this decrease depends on soil type, vegetation cover and snow*. We have read Söyrinki's work and cited it where appropriate, however, we did not find that he explicitly tested the effect of fluctuating temperatures.

@@

We rewrote more clearly in the methods section *Embryo to seed surface area values were calculated by dividing embryo area by the surface area of the seed, more specifically embryo plus endosperm and perisperm. Measurements were made using the ImageJ software (Schneider et al. 2012) on drawings and photographs of seeds cut in half along the longitudinal axis, retrieved mainly from Martin (1946) and the Royal Botanic Gardens Kew Seed Information Database (2017), supplemented with own photographs (Vandelook, unpublished).*. In our opinion this is the most straightforward method to obtain a good perception of the amount of nutrient reserves stored either inside or outside the embryo without going into more advanced 3D methods. It was approximately the same methodology as the one applied by Forbis et al. [-@RN4958].

@@

Trial temperatures are the ones reported in the original datasets, and they correspond to daily temperature regimes programmed in an incubator/growth chamber. For analysis, each trial is represented by two temperature variables: (1) the *average temperature* (i.e. the weighted average of the day and night temperatures, weighted by the duration of each phase) and (2) *alternating temperature* (i.e. a binary variable describing whether the trial applied constant temperature versus different temperatures during the day and the night, in diurnal cycles). These two variables are described later in the text, in the *Description of the dataset* section of the *Results*.

@@

We have removed the adjective *high* and changed the sentence to *yet tolerate heat up to 40–50°C*.

@@

Indeed, this is not something exclusive of alpine environments. We have changed the sentence to *a form of adaptation to unpredictable environments*.

>>>>

---
title: "NPH-MS-2020-34477 - Response to reviewers"
date: "`r format(Sys.time(), '%d/%m/%Y')`"
output: pdf_document
bibliography: refs.bib
csl: new-phytologist.csl
link-citations: yes
always_allow_html: true
---

@@

Thanks for the detailed reviews and the positive feedback. We respond below to all issues pointed out by the referees, grouping comments on similar topics on the same paragraph to facilitate the reading. We have adopted most of the proposed changes. Regarding the use of light, we explain with detail that this is an intrinsic limitation of the meta-analysis, mainly due to the quality of existing data, and discuss the implications. As for the phylogenetic signal, we explain that this is explicitly considered in a phylogenetic comparative statistical method such as the MCMCglmm we used, integrating phylogeny and phylogenetic signal within the analysis.

@@

We have changed the introductory point to a more general and stronger message: *Assumptions about the germination ecology of alpine plants are presently based on individual species and local studies. A current challenge is to synthesize, at the global level, the seed ecological spectrum of alpine plants.*

@@

The effects that are missing are those that overlap with zero (i.e. no effect) and also have very wide credible intervals (much wider than the other cues). They hamper the figure's visibility (i.e. they make all other effects to appear compressed), so we removed them from the plots. We have included this clarification in the figure's caption.

@@

We have moved the call to the section's beginning and labelled the axes. Indicating to which panel we are referring to in the text is not easy, because the different panels/traits are intertwined in the descriptions, therefore it would require to make many recurrent calls (and, in our opinion, that would burden the text too much).

@@

Yes, there is a knowledge gap for tropical mountains. We were unable to find any significant amount of data from the tropics. We have qualified *global* as excluding the tropics throughout the manuscript, and commented on the knowledge gap (and the need of further research in alpine plants of tropical regions) in a new *Future directions* section before the *Conclusions*.

@@

The referee is right that light is a more complex cue than the binary variable we considered. The same can be said about other cues, like alternating temperature (amplitude of the alternation, duration of the cycles...) or cold stratification (actual temperature, length...). Unfortunately, most germination studies in the laboratory use this binary treatment, mainly due to the tradition of detecting major germination strategies. This is a limitation of the data that cannot be dealt with in a meta-analysis, thus we need to find a compromise between data quality and quantity. Detailed descriptions of light spectral composition and photoperiod are only available for a very small fraction of the whole dataset. Therefore, we must summarise cues into variables (like light absence/presence) that are routinely recorded in the majority of trials. We have added these considerations to a new *Future directions* section before the *Conclusions*.

@@

We considered storage type as a continuum (i.e. embryo:seed ratio), ranging from species with small embryos with copious endosperm (often referred to as endospermic) to species with no endosperm at all and all nutrient reserves stored in the embryo (often referred to as non-endospermic seeds). To improve understanding, we have included a definition of non-endospermic seeds as *non-endospermic seeds that store nutrients in the cotyledons*. Nevertheless, we note that in any comparative biology analysis, all species traits are phylogenetically confounded. This is why we used a phylogenetic comparative analysis such as the MCMCglmm. The analysis includes, as a random factor, a matrix of phylogenetic distances among species. In this way, traits are analysed in relation to the underlying phylogenetic structure of the dataset. In our models, both the trait (seed:endosperm ratio) and phylogeny had significant effects, denoting the effect mentioned by the reviewer. The use of phylogenetic comparative analysis is covered in methods/analysis section.

@@

We agree on the conceptual distinction made by the reviewer, but we are using a different terminology for the same concepts. In particular, we use the definition and classification of dormancy that is currently most used in seed ecology and physiology. This framework is based on two main references: (i) the concept by Vleeshouwers et al. [-@RN3254] that dormancy is an inner seed property ("endodormancy"), which should be separated from the absence of appropriate germination cues in the environment ("ecodormancy"); and the classification system proposed by Baskin & Baskin [-@RN3261] based on previous work by Nikolaeva et al. [-@RN2877], which considers morphological and physical dormancy separated from physiological. There are two practical reasons to use this framework: first, it will be readily understandable to the widest scope of readers, including seed ecologists used to these terms; and second, this is the same framework used in the largest amount of seed trait data available [@RN3214; @RN4743]. Although we have retained this definition and classification of dormancy, we also have explained how it corresponds to the “endodormancy” and “ecodormancy” terms suggested by the reviewer.

@@

We have revised the entire conclusions paragraph to address these concerns, being more specific about both the conclusions and about the limitations of the data. In short, we have created a separate section of *Future directions* where we discuss (a) the need to account for phylogenetic constraints and interactions between seed morphology and physiology (citing specific traits/response) in future research; (b) that our results are valid for temperate regions, but little is known about the response of non-seasonal tropical mountains; and (c) that our meta-analysis shows that understanding seed germination of alpine plants still needs more detailed data for major environmental cues. In a final *Conclusions* section we now provide a more concrete take home message: (d) while alpine plants do not show a unique germination syndrome, they do show a more extreme or specialized version of the cold-adapted temperate herb germination syndrome (suggesting convergence).

@@

The referee is right, and we have screened the text to detect these words. *Change* is used either to refer to a concept like climate change, or to encompass and summarise changes that can go in different directions (environmental changes, snow cover changes). *Interplay* and *intertwined* are used in places like the summary and conclusions, where we must summarise concepts that are detailed elsewhere. *Interaction* is used in its statistical meaning, and qualified as *no interaction*, *negative interaction*, etc. We could not find *vary*. Regarding the specific point at L523, this is not a neutral statement: the direction of *interplay* is explained in the same sentence, after the *;* (we have now substituted *;* with *:*).

@@

Thanks for this remark. We have removed wind.

@@

Many of the co-authors generally agree with this view. In any case, this is not the aim of the study, so we have removed from the introduction our comments remarking the importance of regeneration for the general assessment of climate-warming effects on biodiversity. In the new version, the two introductory sentences link directly to former L73.

@@

To the latter. To be more concrete, we have changed the sentence to *Despite the high micro-climatic heterogeneity of alpine landscapes, current assumptions about germination ecology of alpine plants are mainly based on local studies (reviewed in the following paragraphs)*.

@@

We have removed the reference to a hard set depth boundary. The depth profile of temperature fluctuations will depend on soil type, vegetation cover, snow cover. Specifically, the insulating effect of snow cover means that fluctuation of T is not necessarily the norm. We have changed the sentence to *Fluctuations of diurnal temperature decrease with increasing burial depths and the depth profile of this decrease depends on soil type, vegetation cover and snow*. The German-speaking coauthors have revised Söyrinki's work and we have cited it where appropriate, however, we did not find that he explicitly tested the effect of fluctuating temperatures.

@@

We rewrote more clearly in the methods section *Embryo to seed surface area values were calculated by dividing embryo area by the surface area of the seed, more specifically embryo plus endosperm and perisperm. Measurements were made using the ImageJ software (Schneider et al. 2012) on drawings and photographs of seeds cut in half along the longitudinal axis, retrieved mainly from Martin (1946) and the Royal Botanic Gardens Kew Seed Information Database (2017), supplemented with own photographs (Vandelook, unpublished).* In our opinion this is the most straightforward method to obtain a good perception of the amount of nutrient reserves stored either inside or outside the embryo without going into more advanced 3D methods. It was approximately the same methodology as the one applied by Forbis et al. [-@RN4958].

@@

Trial temperatures are the ones reported in the original datasets, and they correspond to daily temperature regimes programmed in an incubator/growth chamber. For analysis, each trial is represented by two temperature variables: (1) the *average temperature* (i.e. the weighted average of the day and night temperatures, weighted by the duration of each phase) and (2) *alternating temperature* (i.e. a binary variable describing whether the trial applied constant temperature versus different temperatures during the day and the night, in diurnal cycles). These two variables are described later in the text, in the *Description of the dataset* section of the *Results*. The other comments of the reviewer are very interesting, we have mentioned a few of them in the *Future directions* section.

@@

We have removed the adjective *high* and changed the sentence to *yet tolerate heat up to 40–50°C*. We are not aware of evidence suggesting that seedlings are more sensitive to high temperatures than adult tissue.

@@

Indeed, this is not exclusive of alpine environments. We have changed the sentence to *a form of adaptation to unpredictable environments*.
